Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-13 paper.qmd
Fix issues

```{r}
num_bins_x_scurve <- 6
num_bins_y_scurve <- 14
hex_size_scurve <- 0.13

hb_obj_scurve <- hex_binning(data = umap_scurve_scaled, x = "UMAP1", 
                      y = "UMAP2", num_bins_x = num_bins_x_scurve, 
                      num_bins_y = num_bins_y_scurve, x_start = NA, y_start = NA, 
                      buffer_x = 0.346, buffer_y = 0.3, hex_size = hex_size_scurve, 
                      col_start = "UMAP")

@@

- NLDR view used to illustrate clusters
- Use our method to assess is it a reasonable representation
- Demonstrate that it is not
- Illustrate how to use out method to get a better representation

>>>>

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 6
num_bins_y_scurve <- 14
hex_size_scurve <- 0.13
buffer_x_scurve <- 0.338
buffer_y_scurve <- 0.292
x_start_scurve <- -0.113
y_start_scurve <- -0.098

## Hexagonal bining to have regular hexagons
hb_obj_scurve <- hex_binning(data = umap_scurve_scaled, x = "UMAP1",
                      y = "UMAP2", num_bins_x = num_bins_x_scurve,
                      num_bins_y = num_bins_y_scurve, x_start = x_start_scurve,
                      y_start = y_start_scurve, buffer_x = buffer_x_scurve,
                      buffer_y = buffer_y_scurve, hex_size = hex_size_scurve,
                      col_start = "UMAP")

@@

- NLDR view used to illustrate clusters
- Use our method to assess is it a reasonable representation
- Demonstrate that it is not
- Illustrate how to use our method to get a better representation
